---
title: "Examining the Top of the League"
output: html_notebook
---

Are there fluctuations in the amount of all-time great players at performing at the top of the league in any given year?

```{r, include = FALSE}
# Libraries
library(tidyverse)

# Import data
season <- read.csv("../data/all_qualified_batter_seasons_fangraphs.csv", stringsAsFactors = FALSE)
colnames(season)[1] <- "Season"

career <- read.csv("../data/career_war_200_PA_min_fangraphs.csv", stringsAsFactors = FALSE)
colnames(career)[1] <- "Name"
```

```{r}
# Create binary variable denoting players with greater than 50 career war
career <- career %>% select(Name, G, PA, WAR, playerid) %>% mutate(WAR_50_greater = ifelse(WAR >= 50, 1, 0), 
                            WAR_20_less = ifelse(WAR <= 20, 1, 0))
```


```{r}
getwd()
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
